---
title: "Education, Child Marriage, and Heterogeneous Wage Returns among Women in Nigeria"
subtitle: "Results"
author: "Hernando Grueso, Ritapriya Bandyopadhyay, Chris Desmond, Brendan Maughan-Brown, Lucie Cluver, William Rudgard"
date: today
date-format: "DD/MM/YYYY"
format:
  beamer:
    theme: default
    colortheme: seahorse
    fonttheme: professionalfonts
    aspectratio: 169
    fig-width: 9
    fig-height: 5
    fig-dpi: 300
    toc: false
    keep-tex: true
    latex-auto-install: true
    header-includes: |
      \usepackage{booktabs}
      \usepackage{longtable}
      \usepackage{array}
      \usepackage{multirow}
      \usepackage{float}
      \usepackage{xcolor}
      \usepackage{adjustbox}
      \usepackage{threeparttable}
      \usepackage{helvet}
      \renewcommand{\familydefault}{\sfdefault}
      \definecolor{darkblue}{HTML}{2C3E50}
      \setbeamercolor{frametitle}{bg=darkblue, fg=white}
      \setbeamercolor{title}{fg=darkblue}
      \setbeamercolor{section in toc}{fg=darkblue}
      \setbeamercolor{structure}{fg=darkblue}
      \setbeamercolor{section in head/foot}{bg=darkblue, fg=white}
      \setbeamertemplate{footline}[frame number]
      \setbeamerfont{footnote}{size=\tiny}
      \setbeamerfont{frametitle}{size=\large}
      \setbeamertemplate{navigation symbols}{}
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(tidyverse)
library(modelsummary)
library(sampleSelection)
library(kableExtra)
library(patchwork)

tidy.heck_wrap   <- function(x, ...) x$tidy_df
glance.heck_wrap <- function(x, ...) x$glance_df

load("outputs/analysis_results.RData")

nat <- results_national
nth <- results_north

# Backward compat: reconstruct df_work if missing
if (is.null(nat$df_work)) {
  nat$df_work <- nat$df_seq %>% filter(has_wage_job == 1 & !is.na(ln_wage_final))
  nth$df_work <- nth$df_seq %>% filter(has_wage_job == 1 & !is.na(ln_wage_final))
}

ms_stars <- c('*' = 0.1, '**' = 0.05, '***' = 0.01)

gof_compact <- tribble(
  ~raw,        ~clean, ~fmt,
  "nobs",      "N",    0,
  "r.squared", "R2",   3
)

gof_probit <- tribble(
  ~raw,   ~clean,         ~fmt,
  "nobs", "Observations", 0
)

cm_probit_slide <- c(
  "years_c" = "Years of Schooling", "years_c2" = "Years Sq.",
  "exp_c" = "Experience", "exp_c2" = "Experience Sq.",
  "child_marriage" = "Child Marriage", "is_rural" = "Rural"
)

rows_p <- tribble(~term, ~`Pr(Wage Work)`, "State FE", "Yes", "Parent Education", "Yes")

cm_lev <- c("edu_primary" = "Primary", "edu_secondary" = "Secondary",
            "edu_higher" = "Higher Ed", "exp_c" = "Experience",
            "exp_c2" = "Experience Sq.", "child_marriage" = "Child Marriage")

cm_lit <- c("is_literate" = "Literate", "exp_c" = "Experience",
            "exp_c2" = "Experience Sq.", "child_marriage" = "Child Marriage")

# Table helper: scale_down + threeparttable for wrapped notes
kb <- function(tbl, sz = 7) {
  tbl %>% kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    font_size = sz
  )
}

# Variable label mapping for tables with raw names
var_labels <- c(
  "child_marriage" = "Child Marriage",
  "years_c" = "Years of Schooling",
  "years_c2" = "Years of Schooling Sq.",
  "exp_c" = "Experience",
  "exp_c2" = "Experience Sq.",
  "is_rural" = "Rural",
  "experience" = "Experience",
  "age" = "Age",
  "father_edu" = "Father's Education",
  "mother_edu" = "Mother's Education",
  "mean.forest.prediction" = "Mean Forest Prediction",
  "differential.forest.prediction" = "Differential Forest Prediction"
)

# Apply labels to a column
relabel <- function(x) ifelse(x %in% names(var_labels), var_labels[x], x)

# Standard notes (WITHOUT significance stars -- modelsummary adds those)
note_ols <- "Source: NLSS 2018-19. Women aged 18-64 in wage employment. Survey weights applied. Schooling and experience are mean-centred."
note_linear <- "Source: NLSS 2018-19. Women aged 18-64 in wage employment. Survey weights applied."
note_probit <- "Source: NLSS 2018-19. All women aged 18-64 with non-missing covariates. Probit includes schooling (+ sq.), experience (+ sq.), child marriage, urban/rural, parental education (factors), and state FE."

# Descriptive stats helper
desc_col <- function(df) {
  fmt_ms <- function(x) sprintf("%.2f (%.2f)", mean(x, na.rm=T), sd(x, na.rm=T))
  fmt_pct <- function(x) sprintf("%.1f", mean(x, na.rm=T) * 100)

  vals <- c(
    fmt_ms(df$ln_wage_final),
    fmt_ms(df$years_of_schooling),
    fmt_ms(df$age),
    fmt_ms(df$experience),
    fmt_pct(df$child_marriage),
    fmt_pct(df$is_rural),
    fmt_pct(df$is_literate),
    fmt_pct(df$currently_married)
  )

  rel <- df %>% count(religion_fac) %>% mutate(pct = n/sum(n)*100)
  islam_pct <- sum(rel$pct[as.character(rel$religion_fac) == "1"], na.rm=T)
  christian_pct <- sum(rel$pct[as.character(rel$religion_fac) == "2"], na.rm=T)
  other_pct <- 100 - islam_pct - christian_pct
  vals <- c(vals, sprintf("%.1f", islam_pct), sprintf("%.1f", christian_pct), sprintf("%.1f", other_pct))

  f_num <- as.numeric(as.character(df$father_edu_fac))
  vals <- c(vals,
    sprintf("%.1f", mean(f_num == 0, na.rm=T) * 100),
    sprintf("%.1f", mean(f_num %in% 1:2, na.rm=T) * 100),
    sprintf("%.1f", mean(f_num >= 3, na.rm=T) * 100))

  m_num <- as.numeric(as.character(df$mother_edu_fac))
  vals <- c(vals,
    sprintf("%.1f", mean(m_num == 0, na.rm=T) * 100),
    sprintf("%.1f", mean(m_num %in% 1:2, na.rm=T) * 100),
    sprintf("%.1f", mean(m_num >= 3, na.rm=T) * 100))

  sec <- df %>% count(sector_fac) %>% mutate(pct = n/sum(n)*100)
  urban_pct <- sum(sec$pct[as.character(sec$sector_fac) == "1"], na.rm=T)
  rural_pct <- sum(sec$pct[as.character(sec$sector_fac) == "0"], na.rm=T)
  vals <- c(vals, sprintf("%.1f", urban_pct), sprintf("%.1f", rural_pct))

  vals <- c(vals, format(nrow(df), big.mark=","))
  vals
}

desc_vars <- c(
  "Log annual wage", "Years of schooling", "Age", "Experience",
  "Child marriage (%)", "Rural (%)", "Literate (%)", "Currently married (%)",
  "Religion: Islam (%)", "Religion: Christianity (%)", "Religion: Other (%)",
  "Father edu: None (%)", "Father edu: Primary (%)", "Father edu: Secondary+ (%)",
  "Mother edu: None (%)", "Mother edu: Primary (%)", "Mother edu: Secondary+ (%)",
  "Sector: Urban (%)", "Sector: Rural (%)",
  "N"
)
```

## Abstract

\small

Early marriage remains widespread in Northern Nigeria and may constrain women's
economic gains from schooling. Using the 2018--19 Nigeria Living Standards Survey
(n=`r format(nrow(nat$plot_cf), big.mark=",")` wage earners nationally;
n=`r format(nrow(nth$plot_cf), big.mark=",")` in Northern Nigeria), we estimate Mincerian wage models with
state fixed effects, Heckman selection correction, and causal forests.

Each additional year of schooling raises wages by **\~15\%** in both samples, with **convex** returns.
Child marriage (before 18) is associated with a
**`r sprintf("%.1f", abs(coef(nat$models_quad[["+ Interaction"]])[["child_marriage"]]) * 100)`\% wage penalty** nationally (12\% prevalence) and
**`r sprintf("%.1f", abs(coef(nth$models_quad[["+ Interaction"]])[["child_marriage"]]) * 100)`\%** in Northern Nigeria (23\% prevalence).

Nationally, the interaction is **significant** (p<0.001): child marriage
reduces both wage levels *and* returns to education. In Northern Nigeria, child marriage
operates as a **pure level shift** (interaction p=0.459).

## Main Results

\small

:::::: {.columns}
::: {.column width="50%"}
### Whole Country (12\% prevalence)

- **Significant interaction** (p < 0.001)
- Child marriage = level shift + reduces returns
- Returns: 7--9\% (married) vs 4--14\% (unmarried)
- Variable importance: 6.8\%
:::

::: {.column width="50%"}
### Northern Nigeria (23\% prevalence)

- **No interaction** (p = 0.459)
- Child marriage = pure level shift
- Returns stay \~15\% regardless of marriage age
- Variable importance: only 4.9\%
:::
::::::

## Policy Implications

\small

1. Each year of schooling raises wages by \~15\%, and child marriage lowers wage
   levels by \~15\%. In Northern Nigeria, these effects are **additive**: policies
   must scale up schooling and delay marriage in parallel.

2. Northern Nigeria's child marriage prevalence (23\%) and wage penalty (\~15\%)
   are roughly **double** the national averages.

3. In high-prevalence settings, the penalty likely reflects broad social
   constraints (fertility timing, mobility limits, norms), calling for
   **community-wide and cash-plus** approaches.

# Descriptive Statistics

## Table 1: Descriptive Statistics (Wage Earners)

```{r}
nat_col <- desc_col(nat$df_work)
nth_col <- desc_col(nth$df_work)

tab1 <- tibble(Variable = desc_vars, National = nat_col, `N. Nigeria` = nth_col)
names(tab1)[2] <- paste0("National (N=", format(nrow(nat$df_work), big.mark=","), ")")
names(tab1)[3] <- paste0("N. Nigeria (N=", format(nrow(nth$df_work), big.mark=","), ")")

tab1 %>%
  kbl(booktabs = TRUE, caption = "Descriptive Statistics -- Wage Earners") %>%
  kb(sz = 4) %>%
  pack_rows("Continuous: Mean (SD)", 1, 4) %>%
  pack_rows("Binary (%)", 5, 8) %>%
  pack_rows("Religion (%)", 9, 11) %>%
  pack_rows("Father education (%)", 12, 14) %>%
  pack_rows("Mother education (%)", 15, 17) %>%
  pack_rows("Sector (%)", 18, 19) %>%
  footnote(general = "Source: NLSS 2018-19. Women aged 18-64 in wage employment. Survey weights applied. Continuous variables: Mean (SD).",
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

# National Results

## Sample Construction -- National

```{r}
nat$sample_flow %>%
  kbl(booktabs = TRUE, caption = "Sample Construction -- National",
      format.args = list(big.mark = ",")) %>%
  kb(sz = 8)
```

## Table 2: National -- Quadratic Mincer

```{r}
modelsummary(
  nat$models_quad,
  stars = ms_stars,
  coef_map = nat$cm_quadratic,
  gof_map = nat$gof_map,
  add_rows = nat$rows_quad,
  title = "National -- Quadratic Mincer",
  output = "kableExtra"
) %>% kb(sz = 4) %>%
  footnote(general = note_ols,
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 3: National -- Linear Specification

```{r}
modelsummary(
  nat$models_lin,
  stars = ms_stars,
  coef_map = nat$cm_linear,
  gof_map = nat$gof_map,
  add_rows = nat$rows_lin,
  title = "National -- Linear Specification",
  output = "kableExtra"
) %>% kb(sz = 4) %>%
  footnote(general = note_linear,
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 4: Returns by Education Level -- National

```{r}
modelsummary(
  list("By Level" = nat$m_lev),
  stars = ms_stars,
  coef_map = cm_lev,
  gof_map = gof_compact,
  title = "Returns by Education Level -- National",
  output = "kableExtra"
) %>% kb(sz = 7) %>%
  footnote(general = paste0("Omitted: No education. State FE, rural, marital controls included. ", note_ols),
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 5: Returns to Literacy -- National

```{r}
modelsummary(
  list("Literacy" = nat$m_lit),
  stars = ms_stars,
  coef_map = cm_lit,
  gof_map = gof_compact,
  title = "Returns to Literacy -- National",
  output = "kableExtra"
) %>% kb(sz = 7) %>%
  footnote(general = paste0("State FE, rural, marital controls included. ", note_ols),
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 6: Probit -- National

```{r}
if (!is.null(nat$probit)) {
  modelsummary(
    list("Pr(Wage Work)" = nat$probit),
    stars = ms_stars,
    coef_map = cm_probit_slide,
    gof_map = gof_probit,
    add_rows = rows_p,
    title = "Probit: Pr(Wage Employment) -- National",
    output = "kableExtra"
  ) %>% kb(sz = 5) %>%
    footnote(general = note_probit,
             general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
}
```

## Table 7: Average Marginal Effects -- National

```{r}
if (!is.null(nat$probit_me)) {
  me_df_nat <- nat$probit_me %>%
    select(factor, AME, SE, p) %>%
    mutate(
      AME = round(AME, 4),
      SE = ifelse(is.na(SE), "---", sprintf("%.4f", SE)),
      p = case_when(is.na(p) ~ "---", p < 0.001 ~ "< 0.001", TRUE ~ sprintf("%.3f", p))
    ) %>%
    rename(Variable = factor)

  me_df_nat %>%
    mutate(Variable = relabel(Variable)) %>%
    kbl(booktabs = TRUE, caption = "Average Marginal Effects on Pr(Wage Work) -- National") %>%
    kb(sz = 7) %>%
    row_spec(which(relabel(me_df_nat$Variable) == "Child Marriage"), bold = TRUE) %>%
    footnote(general = paste0(note_probit, " AME via marginaleffects package."),
             general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
}
```

## Table 8: Causal Forest -- National

:::::: {.columns}
::: {.column width="55%"}

**Average Return to Education**

```{r}
nat$ate_df %>%
  kbl(booktabs = TRUE, digits = 3, caption = "CF: Average Treatment Effect -- National") %>%
  kb(sz = 6) %>%
  footnote(general = "Outcome: Log Annual Wage. Treatment: Years of Schooling. 4,000 trees.",
           general_title = "", threeparttable = TRUE, footnote_as_chunk = TRUE)
```

\vspace{0.2cm}
**Test for Heterogeneity**

```{r}
nat$calib_df %>%
  mutate(Term = relabel(Term)) %>%
  kbl(booktabs = TRUE, digits = 3, caption = "CF Calibration Test -- National") %>%
  kb(sz = 6)
```

:::

::: {.column width="45%"}
**Variable Importance**

```{r}
nat$imp_df %>%
  mutate(Variable = relabel(Variable)) %>%
  kbl(booktabs = TRUE, digits = 3, caption = "CF Variable Importance -- National") %>%
  kb(sz = 6)
```
:::
::::::

## Figure 1: Heterogeneous Returns -- National

```{r}
#| fig-width: 9
#| fig-height: 5
nat$p_cf_main + theme(text = element_text(size = 12)) +
  labs(title = "Figure 1: Heterogeneous Returns to Education -- National")
```

## Figure 2: Distribution of Returns -- National

```{r}
#| fig-width: 9
#| fig-height: 5
nat$p_cf_density + theme(text = element_text(size = 12)) +
  labs(title = "Figure 2: Distribution of Education Returns -- National")
```

## Figure 3: Returns by Level and Marriage -- National

```{r}
#| fig-width: 9
#| fig-height: 5
nat$p_cf_binned + theme(text = element_text(size = 12)) +
  labs(title = "Figure 3: Returns by Level and Marriage Status -- National")
```

## Figure 4: Validation -- National

```{r}
#| fig-width: 9
#| fig-height: 5
nat$p_cf_scatter + theme(text = element_text(size = 12)) +
  labs(title = "Figure 4: Predicted Returns vs. Wage Outcomes -- National")
```

# Northern Nigeria

## Sample Construction -- Northern Nigeria

```{r}
nth$sample_flow %>%
  kbl(booktabs = TRUE, caption = "Sample Construction -- Northern Nigeria",
      format.args = list(big.mark = ",")) %>%
  kb(sz = 8)
```

## Table 9: Northern Nigeria -- Quadratic Mincer

```{r}
modelsummary(
  nth$models_quad,
  stars = ms_stars,
  coef_map = nth$cm_quadratic,
  gof_map = nth$gof_map,
  add_rows = nth$rows_quad,
  title = "Northern Nigeria -- Quadratic Mincer",
  output = "kableExtra"
) %>% kb(sz = 4) %>%
  footnote(general = note_ols,
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 10: Northern Nigeria -- Linear Specification

```{r}
modelsummary(
  nth$models_lin,
  stars = ms_stars,
  coef_map = nth$cm_linear,
  gof_map = nth$gof_map,
  add_rows = nth$rows_lin,
  title = "Northern Nigeria -- Linear Specification",
  output = "kableExtra"
) %>% kb(sz = 4) %>%
  footnote(general = note_linear,
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 11: Returns by Education Level -- N. Nigeria

```{r}
modelsummary(
  list("By Level" = nth$m_lev),
  stars = ms_stars,
  coef_map = cm_lev,
  gof_map = gof_compact,
  title = "Returns by Education Level -- N. Nigeria",
  output = "kableExtra"
) %>% kb(sz = 7) %>%
  footnote(general = paste0("Omitted: No education. State FE, rural, marital controls included. ", note_ols),
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 12: Returns to Literacy -- N. Nigeria

```{r}
modelsummary(
  list("Literacy" = nth$m_lit),
  stars = ms_stars,
  coef_map = cm_lit,
  gof_map = gof_compact,
  title = "Returns to Literacy -- N. Nigeria",
  output = "kableExtra"
) %>% kb(sz = 7) %>%
  footnote(general = paste0("State FE, rural, marital controls included. ", note_ols),
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Table 13: Probit -- N. Nigeria

```{r}
if (!is.null(nth$probit)) {
  modelsummary(
    list("Pr(Wage Work)" = nth$probit),
    stars = ms_stars,
    coef_map = cm_probit_slide,
    gof_map = gof_probit,
    add_rows = rows_p,
    title = "Probit: Pr(Wage Employment) -- N. Nigeria",
    output = "kableExtra"
  ) %>% kb(sz = 5) %>%
    footnote(general = note_probit,
             general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
}
```

## Table 14: Average Marginal Effects -- N. Nigeria

```{r}
if (!is.null(nth$probit_me)) {
  me_df <- nth$probit_me %>%
    select(factor, AME, SE, p) %>%
    mutate(
      AME = round(AME, 4),
      SE = ifelse(is.na(SE), "---", sprintf("%.4f", SE)),
      p = case_when(is.na(p) ~ "---", p < 0.001 ~ "< 0.001", TRUE ~ sprintf("%.3f", p))
    ) %>%
    rename(Variable = factor)

  me_df %>%
    mutate(Variable = relabel(Variable)) %>%
    kbl(booktabs = TRUE, caption = "Average Marginal Effects on Pr(Wage Work) -- N. Nigeria") %>%
    kb(sz = 7) %>%
    row_spec(which(relabel(me_df$Variable) == "Child Marriage"), bold = TRUE) %>%
    footnote(general = paste0(note_probit, " AME via marginaleffects package."),
             general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
}
```

## Table 15: Causal Forest -- N. Nigeria

:::::: {.columns}
::: {.column width="55%"}

**Average Return to Education**

```{r}
nth$ate_df %>%
  kbl(booktabs = TRUE, digits = 3, caption = "CF: Average Treatment Effect -- N. Nigeria") %>%
  kb(sz = 6) %>%
  footnote(general = "Outcome: Log Annual Wage. Treatment: Years of Schooling. 4,000 trees.",
           general_title = "", threeparttable = TRUE, footnote_as_chunk = TRUE)
```

\vspace{0.2cm}
**Test for Heterogeneity**

```{r}
nth$calib_df %>%
  mutate(Term = relabel(Term)) %>%
  kbl(booktabs = TRUE, digits = 3, caption = "CF Calibration Test -- N. Nigeria") %>%
  kb(sz = 6)
```

:::

::: {.column width="45%"}
**Variable Importance**

```{r}
nth$imp_df %>%
  mutate(Variable = relabel(Variable)) %>%
  kbl(booktabs = TRUE, digits = 3, caption = "CF Variable Importance -- N. Nigeria") %>%
  kb(sz = 6)
```
:::
::::::

## Figure 5: Heterogeneous Returns -- N. Nigeria

```{r}
#| fig-width: 9
#| fig-height: 5
nth$p_cf_main + theme(text = element_text(size = 12)) +
  labs(title = "Figure 5: Heterogeneous Returns to Education -- N. Nigeria")
```

## Figure 6: Distribution of Returns -- N. Nigeria

```{r}
#| fig-width: 9
#| fig-height: 5
nth$p_cf_density + theme(text = element_text(size = 12)) +
  labs(title = "Figure 6: Distribution of Education Returns -- N. Nigeria")
```

## Figure 7: Returns by Level and Marriage -- N. Nigeria

```{r}
#| fig-width: 9
#| fig-height: 5
nth$p_cf_binned + theme(text = element_text(size = 12)) +
  labs(title = "Figure 7: Returns by Level and Marriage Status -- N. Nigeria")
```

## Figure 8: Validation -- N. Nigeria

```{r}
#| fig-width: 9
#| fig-height: 5
nth$p_cf_scatter + theme(text = element_text(size = 12)) +
  labs(title = "Figure 8: Predicted Returns vs. Wage Outcomes -- N. Nigeria")
```

# Cross-Region Comparison

## Figure 9: Returns Across Methods -- National

```{r}
#| fig-width: 11
#| fig-height: 5
nat$p_panel + theme(text = element_text(size = 11)) +
  plot_annotation(title = "Figure 9: Returns Across Methods -- National")
```

## Figure 10: Returns Across Methods -- N. Nigeria

```{r}
#| fig-width: 11
#| fig-height: 5
nth$p_panel + theme(text = element_text(size = 11)) +
  plot_annotation(title = "Figure 10: Returns Across Methods -- N. Nigeria")
```

## Table 16: Key Estimates Comparison

```{r}
compare <- tibble(
  Metric = c(
    "Average Return (CF)",
    "Return Std. Error",
    "Child Marriage Penalty (OLS+FE)",
    "Interaction: Years x Child Marriage",
    "Interaction p-value",
    "Child Marriage Var. Importance (CF)",
    "Heckman lambda",
    "N (wage earners)",
    "N (selection sample)"
  ),
  National = c(
    sprintf("%.1f%%", nat$ate["estimate"] * 100),
    sprintf("%.3f", nat$ate["std.err"]),
    sprintf("%.1f%%", coef(nat$models_quad[["+ State FE"]])[["child_marriage"]] * 100),
    sprintf("%.3f", coef(nat$models_quad[["+ Interaction"]])[["years_c:child_marriage"]]),
    "< 0.001",
    sprintf("%.1f%%", nat$imp_df$Importance[nat$imp_df$Variable == "child_marriage"] * 100),
    "0.822**",
    format(nrow(nat$plot_cf), big.mark = ","),
    format(nrow(nat$df_seq), big.mark = ",")
  ),
  `N. Nigeria` = c(
    sprintf("%.1f%%", nth$ate["estimate"] * 100),
    sprintf("%.3f", nth$ate["std.err"]),
    sprintf("%.1f%%", coef(nth$models_quad[["+ State FE"]])[["child_marriage"]] * 100),
    sprintf("%.3f", coef(nth$models_quad[["+ Interaction"]])[["years_c:child_marriage"]]),
    "0.459",
    sprintf("%.1f%%", nth$imp_df$Importance[nth$imp_df$Variable == "child_marriage"] * 100),
    "0.217 (n.s.)",
    format(nrow(nth$plot_cf), big.mark = ","),
    format(nrow(nth$df_seq), big.mark = ",")
  )
)

compare %>%
  kbl(booktabs = TRUE, caption = "Key Estimates -- National vs. Northern Nigeria") %>%
  kb(sz = 6) %>%
  row_spec(5, bold = TRUE) %>%
  footnote(general = "Source: NLSS 2018-19. CF = Causal Forest. OLS+FE = OLS with state fixed effects.",
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```

# Appendix

## Table A1: Descriptive Statistics (Full Working-Age Sample)

```{r}
nat_full <- desc_col(nat$df_seq)
nth_full <- desc_col(nth$df_seq)

tabA1 <- tibble(Variable = desc_vars, National = nat_full, `N. Nigeria` = nth_full)

# Add wage employment row before N
wage_row <- tibble(
  Variable = "Wage employment (%)",
  National = "8.7",
  `N. Nigeria` = "5.6"
)
names(wage_row) <- names(tabA1)
tabA1 <- bind_rows(tabA1[1:19,], wage_row, tabA1[20,])

names(tabA1)[2] <- paste0("National (N=", format(nrow(nat$df_seq), big.mark=","), ")")
names(tabA1)[3] <- paste0("N. Nigeria (N=", format(nrow(nth$df_seq), big.mark=","), ")")

tabA1 %>%
  kbl(booktabs = TRUE, caption = "Descriptive Statistics -- Full Working-Age Sample") %>%
  kb(sz = 4) %>%
  pack_rows("Continuous: Mean (SD)", 1, 4) %>%
  pack_rows("Binary (%)", 5, 8) %>%
  pack_rows("Religion (%)", 9, 11) %>%
  pack_rows("Father education (%)", 12, 14) %>%
  pack_rows("Mother education (%)", 15, 17) %>%
  pack_rows("Sector (%)", 18, 19) %>%
  pack_rows("Labour market (%)", 20, 20) %>%
  footnote(general = "Source: NLSS 2018-19. All women aged 18-64 with non-missing covariates (used in first-stage probit). Survey weights applied.",
           general_title = "Note: ", footnote_as_chunk = TRUE, threeparttable = TRUE)
```
